\documentclass[a5paper]{scrartcl}
\usepackage{amssymb, amsmath} % needed for math
\usepackage[utf8]{inputenc} % this is needed for umlauts
\usepackage[USenglish]{babel} % this is needed for umlauts
\usepackage[T1]{fontenc}    % this is needed for correct output of umlauts in pdf
%\usepackage[margin=2.5cm]{geometry} %layout
\usepackage{hyperref}   % links im text
\usepackage{csquotes}
\usepackage{stackengine}
\usepackage{graphicx}
\def\asterism{\par\vspace{1em}{\centering\scalebox{1.5}{%\\
  \stackon[-0.5pt]{\bfseries*~*}{\bfseries*}}\par}\vspace{.5em}\par}

\usepackage{yfonts,color}
\usepackage{microtype}

\title{The Afterlife Experiment}
\author{The Dalek Emperor}

\hypersetup{
  pdfauthor   = {The Dalek Emperor},
  pdfkeywords = {},
  pdftitle    = {The Afterlife Experiment}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\\
% Begin document                                                    %\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\\
\begin{document}
\maketitle

\yinipar{\color{black}I}'ve always felt a little lost in life, like I never received complete instructions on who I'm supposed to be. Everyone else around me seemed to know exactly who they were. Their lives would fly right by me; their GPS's locked on to destinations while I just sat idling in the street. In high school I never did any extracurricular activities because I couldn't figure out if I was a sports person or a music person. And it was no different in college. I wandered through four different majors, unable to decide who I wanted to be. I just felt like a blank slate.\\
And if I was a blank slate, Micah York was The Starry Night - authentic, beautiful, perfect. He was my exact antithesis which is what attracted me to him in the first place. He was born knowing \textit{exactly} who he was and what he was about. His confidence and certainty in himself was an all but tangible element of him.\\
We first met in our freshman year of college; he was a neuroscience student and I was majoring in History. We dated our sophomore year, after I changed my major to Nanotechnology. We broke up in our junior year, just before I decided I wanted a degree in Psychology, instead. And he asked me a favor our senior year, just after my guidance counselor told me it was too late to switch majors again.\\
Our last semester of college was beginning soon and Micah had been applying to grad schools. He wanted to get his Masters in Neurobiology and I helped him with the applications when I had time. I knew Micah was under a lot of stress to nail his senior thesis so I was surprised when he asked me over to his house for a “party” that January. I should have known something was up because Micah was a meticulous student and he didn't throw parties – ever.\\
When I arrived at his off campus apartment, I considered not even getting out of the car. His flat was dark and quiet, there was definitely no party. Just what was he up to? I picked up my phone to call Micah and beg off but curiosity suddenly got the better of me and I hung up.\\
When I walked into the familiar TV-less living room I saw two familiar faces and two strange ones.\\
There was Micah, of course, and Micah's friend Sean Nichols, an organic chemistry major. The other two people were introduced to me as Irina Bradley, another med student, and Holly Bish, a philosophy major.\\
Irina the med student scooted over and made room for me on the couch. I sat down hesitantly and waited for Micah to begin whatever it was he was doing. He rose and walked to the middle of the room.\\
\enquote{Thank you all for coming. I'm sure you're wondering why you're here. I'm sorry this isn't a party, but I knew I \textit{had} to get you here by any means necessary.}\\
Micah paused, for effect I'm sure, took a deep breath and smiled.\\
\enquote{I have selected each of you to take part in the greatest experiment of not only your lives but perhaps even the \textit{world}. My doctoral thesis.}\\
I rolled my eyes. Classic Micah. He may be many things, but humble wasn't one of them. Jackass was.\\
\enquote{And what's your thesis?} I asked him nonchalantly, as if his previous statement hadn't been utterly stupid.\\
\enquote{A conclusive essay detailing what happens after human death.}\\
Irina the med student laughed.\\
Micah bristled but stayed silent. Sadly, I knew him well enough to know he was serious.\\
\enquote{How do you intend to prove anything?} I asked. \enquote{What kind of experiments will you be doing?}\\
\enquote{Well, Bridget, I'm going to kill myself.}\\
The room fell quiet and Micah, mistaking the shocked horror for awed silence, stood up a little taller and held out a hand silencing any questions.\\
\enquote{You can't be serious.}\\
\enquote{Oh, I am and it's completely safe. I am going to be the first person in the world to prove or disprove the existence of an afterlife.}\\
\enquote{We,} demanded Sean.\\
\enquote{Yes, we. This paper is going to be our ticket into any university in the country. The world even! There are wars being fought everyday over deities and religions and we are going to be the ones to prove what is scientifically correct beyond a shadow of a doubt!}\\
\enquote{You're an idiot,} I sighed and rose from the couch to leave. Irina followed me but Micah beat us to the door.\\
\enquote{Bridget, wait! At least hear all of it before you walk away. Please.}\\
I narrowed my eyes at him and considered. Micah was crazy, beyond crazy, but he was also brilliant. And he looked\dots sane, somehow, like he knew what he was doing. But still, I wanted no part in killing anyone.\\
\enquote{I'd like to hear how it works.} Holly the philosophy major said coolly from her spot on the couch.\\
\enquote{Ah, actually, it's something \textit{I} developed.} Sean said. \enquote{A cocktail of biological and non-biological chemicals. It's been tested and it's safe.}\\
\enquote{\textit{Tested?}} I asked in horror. \enquote{On whom?}\\
\enquote{On local wildlife.}\\
\enquote{So never on a person.}\\
\enquote{No, never on a person but it \textit{is} safe.} Sean said quickly.\\
\enquote{So then how \textit{does} it work?} Irina asked. She took a step back toward the couch and that's when I knew Micah had her. I took my hand off the door knob.\\
Micah gestured to Sean.\\
\enquote{I've developed a poison and a biologic. I call them the Romeo and Juliet serums. Juliet is a poison that kills the body. Romeo is a biologic, or antidote for lack of a better word, that restarts it.}\\
\enquote{Clinical death will only take place for 30 seconds.” Micah cut in. “No brain damage, no organ damage.}\\
“Yes, it's perfectly safe; the body will only be dead for a short time.” Sean confirmed.\\
\enquote{So, Flatliners.} I said accusingly, glaring at Micah.\\
\enquote{What?} Sean asked.\\
\enquote{Flatliners, it's a movie. The characters kill themselves and bring themselves back. If I recall it didn't work out too well for them. But Micah knows that since he's the one that made me watch it!}\\
\enquote{That's a Hollywood movie.} Micah said, dryly. \enquote{This is legitimate science.}\\
\enquote{No, you're Kevin Bacon,” I pointed at him, “he's Kiefer Sutherland,} I pointed at Sean, \enquote{and I'm Julia fucking Roberts!}\\
\enquote{No,} Micah said hotly, \enquote{actually \enquote{she's} Julia fucking Roberts!} He pointed to Holly.\\
\enquote{So am I Oliver Platt, then?} asked Irina.\\
\enquote{No one is Oliver Platt!} Micah yelled.\\
\enquote{Well, if we get a choice I'd rather be Oliver Platt than Kevin Bacon.} Sean interrupted.\\
\enquote{Sean, you're fucking Kevin Bacon.} Micah spat.\\
\enquote{And you're Keifer Sutherland!} I yelled at him.\\
\enquote{THIS ISN'T FUCKING FLATLINERS!}\\
I sighed. \enquote{So I'm not going under.}\\
\enquote{No.} Micah looked exasperated.\\
\enquote{Then why am I here?}\\
Micah combed his hand through his dark brown hair. \enquote{Jesus, I've been trying to get to that.}\\
\enquote{Am I going under?} Irina asked.\\
\enquote{No, just me, Sean and Holly.}\\
\enquote{And you think she's going to agree with that?}\\
\enquote{Actually,} Holly interrupted, rising from the couch. \enquote{I already have.}\\
\enquote{Why?} I gaped at her.\\
\enquote{Because I want to know, I \textit{need} to know why I'm here, why any of us are here. I want to know what the soul is and where it goes, I want to hold the keys to human existence, love and suffering, life and death. I want to understand our purpose. And I'm getting paid and it's perfect for my dissertation.}\\
\enquote{That's another thing,} Micah said quickly, \enquote{everyone will get paid.}\\
\enquote{How much?} Irina narrowed her eyes at him.\\
\enquote{\$500 each.}\\
I groaned. \$500 was pretty much how short I was on tuition for this semester and Micah knew that. What an ass.\\
\enquote{The Romeo and Juliet serums are safe. They've been tried and tested and they will work. Sean and I have rented a house on Emerald Street to conduct the experiment. All I need, all I'm asking, is for you to show up, Bridget. Just show up next Saturday.}\\
\enquote{And what about me?} asked Irina.\\
\enquote{Irina, I need you to administer the serums and monitor vital signs. Look guys, this whole thing will take less than a minute and then you guys can walk away with your five hundred dollars and a credit on my thesis.}\\
\enquote{And what makes your evidence, which is pretty much just your testimony, conclusive?} I asked.\\
\enquote{The serums Sean developed will be available to anyone and everyone and they can repeat my experiment at their leisure.}\\
“But I don't think that-“\\
\enquote{Please, Bridget, just show up on Saturday.}\\
There wasn't one facet of this little science experiment that didn't make me profoundly uncomfortable. But the way Micah looked at me, the tension in the room, the five hundred dollars\dots\\
\enquote{I'm not asked, Bridget. I'm begging.} Micah grabbed my hands and squeezed.\\
\enquote{I'll think about it.}

\asterism

I wasn't really surprised to find myself at the house on Emerald Street that following Saturday. I'd debated about it all week but in the end - all other factors not withstanding - I was curious. Micah was brilliant, top 1\% of his class, several published papers; what if he was right? What if he did see something? People have near death experiences everyday and came back with stories. Micah was going deeper into death than anyone ever had before and he was doing it in a controlled environment with variables that could be easily duplicated, I mean, who knows?\\
Micah greeted me at the door with a relieved smile and walked me to the large, barren living room. It sported tan walls, hardwood floors, lots of machines and monitors and 3 cheap looking twin beds.\\
Sean and Holly were already laying on two of the beds with nervous smiles on their faces and IVs in their arms. Irina was bustling around checking equipment and looking incredibly stressed.\\
Micah handed me an expensive looking, heavy camera. \enquote{The camera in the corner is already recording - that's our static camera. I need you to walk around and record with this one as well. Irina is going to stagger our injections so that she can handle all three of us. You are simply a witness, nothing more.}\\
\enquote{Okay\dots Micah, are sure you want to do this?}\\
\enquote{Bridget, we've been testing this and as long as Romeo is injected in under a minute, which it will be, there is no risk.}\\
\enquote{There's definitely risk, Micah. And near death experiences-}\\
\enquote{This isn't a \textit{near} death experience, it's a death experiment. Look, I know you're worried, and that's why I wanted you here, to make sure nothing goes wrong. And even if it does, I have stacks and stacks of notes and narratives proving that this was my experiment.}\\
\enquote{Yeah, but\dots}\\
I couldn't think of anything else to say. Any objection I had, Micah would have an answer for. That's just the way he was. There was no stopping him now; I could either be here to see it or be somewhere else to hear about it. I chose to stay.\\
Micah walked over to stand in front of the static camera.\\
“It's 12:51PM on Saturday, January 14th. I am Micah York and this is the first attempt of the afterlife experiment.”\\
Micah walked over to his bed and sat down, letting Irina expertly thread a needle into his vein. He lay back on the pillow with a notebook and pen in hand and turned to Sean and Holly.\\
\enquote{Remember, guys, as soon as you regain consciousness write down everything you remember.}\\
They nodded at him and held up their own notebooks.\\
\enquote{Okay guys,} Irina said with a shaky voice. \enquote{Everything is ready.}\\
\enquote{Alright,” Micah said, excitedly, “30 seconds, that's all. Irina, as soon as the last of the Juliet leaves the tube, hit this timer.}\\
Micah pointed to the digital clocks that were set to 00:30 at the head of each bed. Irina nodded.\\
\enquote{Bridget, you film.} I swallowed loudly and nodded too.\\
\enquote{See you on the other side,} Micah smiled and gave a thumbs up to Holly and Sean who returned it and then settled back on their beds. I hit record.\\
Irina picked up three red tubes of thick, clear liquid from a nearby table. Steadying her hands, she slowly injected the first tube into Micah's IV, and then hit the timer above him. At the exact moment she did, Micah's heart-rate monitor flat-lined. I jumped at the high-pitched squeal and tried to steady the camera.\\
Irina hurriedly moved over to Sean and did the same for him and then Holly. Now all three EKG machines were loudly flat-lining. Irina put her hands over her ears for a minute and then pointed to a different monitor.\\
\enquote{Get this! Bridget, record this!} It was Micah's EEG and there were zero active brain waves. \enquote{Get Holly and Sean's too!}\\
I could suddenly taste a bitter metal in my mouth and I knew I was beginning to panic. This had been a bad idea, a very bad idea. By the time I looked back over to Micah's timer there was 8 seconds left on it. Irina had already loaded up a green tube, the Romeo biologic, to Micah's IV and was just waiting to push it in.\\
The chorus of all three EKG machines wildly sounding their alarms was deafening. It was screaming at us: “Do something! DO something! Why are you just standing there? Save them!”\\
Just when I couldn't stand it anymore, a different alarm buzzed and Irina injected the Romeo into Micah's arm. I didn't breathe at all as I waited for Micah's vital monitors to show life. It took less than 5 seconds for the EKG machine to register a spike. And then another. Micah's EEG machine suddenly flared to life as well. I exhaled.\\
Irina had just stepped over to Sean when Micah suddenly shot up in bed, eyes wide, and opened his mouth. I was so excited and curious that I almost forgot to hold the camera up. I couldn't wait to hear what he had to say.\\
But Micah didn't say anything. He just screamed. The surprise and force of it made me stumble back into a wall. It was the most blood-curling scream I had ever heard. And then, Sean started screaming, too. Micah took no notice of him and threw himself off the bed to the floor, slamming his head on the wood over and over again. Sean had also jumped out of bed and run over to the wall to stand just 2 inches from it, screaming at it, as if he didn't know the wall was there.\\
My shock quickly gave way to panic. Micah's head was already bloody and the sound it made against the hard oak was sickening.\\
\enquote{Irina, help me!}\\
Irina, who hadn't moved since Sean had knocked her out of the way, stared at me wide-eyed.\\
\enquote{We need to get him off the floor, he's hurting himself!}\\
She opened her palm and looked down at the last tube of Romeo biologic as if she'd never seen it before.\\
\enquote{You didn't give that to her yet?! Give that to Holly! Now!} My voice was high and wild. I was holding Micah in my arms while he continued to hit his head against the air, as if the floor were still there. And the screaming, oh God, the screaming.\\
Both Micah and Sean were splitting my ears open. The horror on Micah's face as he beat his head harmlessly against the air, mouth open in a wide O and the sharp, agonizing terror coming out of Sean was enough to make me my eyes well up in fear. What had happened? What had they seen?\\
The camera, long forgotten, lay discarded under Micah's bed where his flailing legs had kicked it. Irina was doing frantic chest compressions on Holly, tears streaming from her eyes. But I knew it was too late, Holly was lost.\\
\enquote{Irina, Irina, call 911.} She didn't stop working on Holly, just continued on like she hadn't heard me. And perhaps she hadn't. The screaming\dots\\
I let go of Micah just for a moment to grab my phone and he was up and running. He hit the front door and smashing his forehead against the glass.\\
\enquote{Micah, stop!}\\
If Sean noticed us near him, he didn't show it. He just continued that piercing, horrible scream.\\
Emergency services couldn't hear me on the phone but they had someone at the house within 5 minutes. A very, very long 5 minutes. Irina gave up on Holly at some point and just paced around the room mumbling \enquote{I don't understand. I did it right. I don't understand.}\\
They took Sean, Holly and Micah away in an ambulance and they took me and Irina to the police station. They watched the videos.\\
I never graduated but at least I didn't go to prison like Irina. I retreated into myself after her trial and refused to speak to anybody. I spent months holed up in my apartment asking the same question over and over.\\
What did they see?\\
And it's not like I could ask them. Sean had screamed until he permanently lost the use of his voice. Now he sits in a room in a hospital facing a wall with his mouth wide open as if he were screaming. And somehow, that's worse than the screaming. He hasn't said or written a word since that day.\\
Micah, he's in a hospital too. Sometimes he screams and sometimes he's quiet. Sometimes he thrashes and sometimes he lies as still as the dead.\\
I have visited them both many times, begging them to tell me what they saw. But my visits were fruitless until this last time.\\
Yesterday when I visited Micah he was in his screaming stage. I sat with him and let him scream waiting to see if he would transition to one of his catatonic stages so that I could speak. When I was tired of waiting I leaned in close to his ear and I asked him.\\
\enquote{Micah, what did you see?}\\
His screaming slowly morphed into an insane, uncontrollable laughter I'd never heard before. His doctor, who'd been just outside, came running into the room.\\
\enquote{What did you do?} He asked, alarmed.\\
\enquote{I just asked him a question.} I responded, quietly.\\
\enquote{What was the question?}\\
\enquote{I asked him what he saw.}\\
We both noticed the sudden silence at the same time. We slowly turned toward Micah to find him facing us, no expression on his face.\\
\enquote{It's waiting for you. It's waiting for all of you.} Then his mouth fell open into a large O and the laughter slowly began again followed by shrill, horrible screams.\\
I left the hospital that day wishing I had never come at all, wishing I'm never met Micah. I drove home with tears pouring down my cheeks. \textit{What did they see? What's on the other side? Do I even want to know?} But it really doesn't matter anymore. Someday I'll find out. And so will you.
\end{document}